\thispagestyle{empty}
\header{\headerforeword}
These guidelines are based on thesis instructions of the former Department of Electrical and Information Engineering, the instructions of the publication series Acta Universitatis Fennica, and the book “Teknisen kirjoituksen laatiminen” \cite{lappalainen, acta, tirronen}. Several persons from the former Department of Electrical and Information Engineering have participated in setting up these instructions. The preparation of the first version was led by Prof. Pentti Lappalainen.

The Finnish guidelines were edited by the Study Committee of the Department of Electrical and Information Engineering in 2005 and 2010-2011, and revised by the Degree Programme Committee of Computer Science and Engineering in 2011 and 2012. The original English version was written by the Degree Programme Committee of Electrical Engineering; this version is based on that version and the Finnish instructions for Computer Science and Engineering. This English version has been updated to comply with the new conventions for archiving the electronic versions of master’s theses in 2013, and the organization renewal in 2016 where the Department of Computer Science and Engineering was disbanded and divided into three research units. 

The instructions were revised in July 2018 for the Faculty of Information Technology and Electrical Engineering. The update was coupled with the transition to Overleaf as recommended \LaTeX\ document preparation platform. The key modification was the overhaul of referencing to IEEE style. \DIFdelbegin \DIFdel{This document is applicable for Bachelor's and Diploma theses completed in and after 2018.
}%DIFDELCMD < 

%DIFDELCMD < %%%
\DIFdel{The latest }\DIFdelend \DIFaddbegin \DIFadd{The }\DIFaddend revisions in 2023 were made by the Computer Engineering Degree Program Committee to improve instructions and to clarify the use of footnotes and references in case of pictures.
\DIFaddbegin 

\DIFadd{The latest revision was done in August 2025. This included a complete
overhaul of the LaTeX template. Stylistic details have been unified
with with the guidelines of the Degree Programme of Electronics and
Communication Engineering, though some differences remain. The
instructions have also improved the instructions on copyright issues,
especially involving images and proper citation style.
}

\DIFadd{This document is applicable for Bachelor's and Diploma theses starting or completing in and after September 2025.
}\DIFaddend 

\signature
